\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-30 article/main.tex
petit ajout sur le process

All of that leaded us to seven main categories.
% explication pour chaque catégorie
\begin{itemize}
	\item \textbf{Detection strategy} : 
	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent.
	\item \textbf{Analysis type}
	\item \textbf{Validation method}
	\item \textbf{Detection Level}
	\item \textbf{Detected pattern types}
	\item \textbf{Pattern detection generality}
\end{itemize}

@@

>>>>

All of that leaded us to seven main categories.

\begin{itemize}
	\item \textbf{Detection strategy} : This determine the means on which the detection is based. It could include Artificial intelligence, machine learning, graph, metrics, logic, automata, instrumentation, pattern matching or others techniques.
	\item \textbf{Language generality} : This specifies if the detection is langage dependent or independent,
	\item \textbf{Analysis type} : This determine if a detection techniques use a static, dynamic or hybrid approach.
	\item \textbf{Validation method} : This specifies the type of scientific validation methods the article's authors used for a detection method.
	\item \textbf{Detection Level} : This define on which level the detection method work : execution, source and model. It could be more than one level for a single method of detection.
	\item \textbf{Detected pattern types} : This characterizes the type of design pattern a specific detection method can manage.
	\item \textbf{Pattern detection generality} : This determine if a method is made to detect a single pattern or more than one pattern.
\end{itemize}

@@

%todo
